Share Buyback and Equity Issue Anomalies Revisited: Interactive Tool

### 2016-02-15 index.Rmd
updating tool

---
title: "Share Buyback and Equity Issue Anomalies Revisited: Interactive Tool"
author: "Theodoros Evgeniou, Enric Junque de Fortuny, Nick Nassuphis, and Theo Vermaelen"
output:  
  html_document:
    fig_width: 6
    fig_height: 2.5
    fig_align: center
runtime: shiny
---

@@

DATASET = BUYBACK_DATA$DATASET

@@

This is an interactive tool for the article **Share Buyback and Equity Issue Anomalies Revisited**. Users can explore the effects of various parameters as well as data sampling choices. For any given choice, users can generate and download a new *customized* version of the paper by clicking the button below at any time:**
<br>
<br>

```{r, fig.width=6, fig.height=5,echo=FALSE}
downloadHandler(
  filename = "report.pdf",
  content = function(file) {
    src <- normalizePath('BBtool_pdf.Rmd')
    # temporarily switch to the temp dir, in case you do not have write
    # permission to the current working directory
    #owd <- setwd(tempdir())
    #on.exit(setwd(owd))
    #file.copy(src, 'ExerciseSet2v2pdf.Rmd')
    #library(rmarkdown)
    out <- render('BBtool_pdf.Rmd', pdf_document(),envir=environment())
    file.rename(out, file)
  }
)
```

This tool allows the user to explore descriptive statistics of some of the key firm characteristics. When the name of the firm characteristics ends with ".Score" it is  either the 1-5 score relative to the Fama-French breakpoints (for Size, Prior returns, and BE/ME ratio) or the percentile relative to all firms in the CRSP universe at the time of the buyback announcement, as discussed in the paper. Otherwise it is the raw values of the firm characteristic.

fluidPage(
  selectInput("characteristic", "Select Firm Characteristic:", choices = acceptaple_features,selected = acceptaple_features[1]),
  mainPanel(
    tabsetPanel("Example",
                tabPanel("Histogram",
                         renderPlot({
                           feature = BUYBACK_DATA$DATASET$SDC[[which(names(BUYBACK_DATA$DATASET$SDC) == input$characteristic)]]
                           feature = feature[!is.na(feature)]
                           if (!is.numeric(feature))
                             feature = 1
                           hist(feature, density = 100, breaks = 100)
                         })),
                tabPanel("Summary Statistics",
                         renderDataTable({
                           feature = BUYBACK_DATA$DATASET$SDC[[which(names(BUYBACK_DATA$DATASET$SDC) == input$characteristic)]]
                           #feature = feature[!is.na(feature)]
                           if (length(unique(feature)) > 20 & is.numeric(feature)){
                             res = t(as.matrix(summary(feature)))
                             colnames(res) <- c("Minimum", "1st Quantile", "Median", "Mean", "3rd Quantile", "Max")
                           }
                           if (is.character(feature) | length(unique(feature)) <= 20){
                             tmp = table(feature)
                             res = t(as.matrix(tmp))
                           }
                           as.data.frame(res)
                           #m1<-gvisTable(show_data,options=list(showRowNumber=TRUE,width=1220, height=min(400,27*(nrow(show_data)+1)),allowHTML=TRUE,page='disable'))
                           #print(m1,'chart')
                         })
                )
    ),style='width: 100%;'))
```

### Robustness Analysis

Two types of robustness analysis has been considered in the paper: over different time periods, and across industries. This tool allows a more detailed robustness analysis along the lines of the results presented in the paper:

@@

The article relates 5 firm characteristics (pre-buyback-announcement returns, idiosyncratic volatility, and volatility, as well as BE/ME and Firm Size). This tool allows the user to study the effects of combining any of these firm characteristics, as well as some other ones not studied in the paper for simplicity.

@@

selectInput("characteristic_irats", "Select Firm Characteristic to Define High/Low Firms:", choices = acceptaple_features1,selected = acceptaple_features1[1])

selectInput("quantile_used","Enter the quantile to use to define High and Low Firms:", choices = 0.02*(1:20), selected = "0.2")

feature_IRATStable <- reactive({
  thefeature = DATASET$SDC[[which(names(DATASET$SDC) == input$characteristic_irats)]]  
  High_feature_events = which(scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used)) & !is.na(thefeature))
  Low_feature_events = which(scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used)) & !is.na(thefeature))
  res = round(cbind(
    car_table(DATASET$returns_by_event_monthly[,Low_feature_events], DATASET$SDC$Event.Date[Low_feature_events], Risk_Factors_Monthly)$results,
    car_table(DATASET$returns_by_event_monthly[,High_feature_events], DATASET$SDC$Event.Date[High_feature_events], Risk_Factors_Monthly)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
  res
})

High_feature_Hedged_react <- reactive({
  thefeature = DATASET$SDC[[which(names(DATASET$SDC) == input$characteristic_irats)]]  
  High_feature_events = which(scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used)) & !is.na(thefeature))
  High_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", High_feature_events,  DATASET$DatesMonth, DATASET$returns_by_event_monthly,event=1),1,non_zero_mean)
  remove_initialization_time(suppressWarnings(scrub(alpha_lm(High_feature,Risk_Factors_Monthly[,pnl_hedge_factors],hedge_months,trade=1))),min_date=FirstTrade)
})

Low_feature_Hedged_react <- reactive({
  thefeature = DATASET$SDC[[which(names(DATASET$SDC) == input$characteristic_irats)]]  
  Low_feature_events = which(scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used)) & !is.na(thefeature))
  Low_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", Low_feature_events,  DATASET$DatesMonth, DATASET$returns_by_event_monthly,event=1),1,non_zero_mean)
  remove_initialization_time(suppressWarnings(scrub(alpha_lm(Low_feature,Risk_Factors_Monthly[,pnl_hedge_factors],hedge_months,trade=1))),min_date=FirstTrade)  
})

@@

```{r, eval=TRUE, echo = FALSE}
fluidPage(
  mainPanel(
    tabsetPanel("Example",
                tabPanel("Five-Factor IRATS Cumulative Abnormal Returns",
                         renderTable({
                           feature_IRATStable()
                         })),
                tabPanel("Cumulative Abnormal Returns,High, 12m hold",
                         renderDygraph({
                           pnl_plot_interactive(High_feature_Hedged_react())
                         })),
                tabPanel("Monthly and Yearly Returns, High, 12m hold",
                         renderUI({
                           renderHeatmapX(pnl_matrix(High_feature_Hedged_react()))
                         })
                )
    ),style='width: 100%;'))
```

### Customizable Buyback Index

Must like the EU-index in the paper, one can create other indices by combining different firm characteristics as needed.

@@

<br>
```{r, eval=TRUE, echo = FALSE}
selectInput("characteristic_irats1", "Select First Firm Characteristic for your new index:", choices = acceptaple_features2,selected = acceptaple_features2[1], width = "1000px")
```

selectInput("characteristic_irats2", "Select Second Firm Characteristic for your new index:", choices = acceptaple_features2,selected ="None", width = "1000px")
```

selectInput("characteristic_irats3", "Select Third Firm Characteristic for your new index:", choices = acceptaple_features2,selected = "None", width = "1000px")
```

selectInput("characteristic_irats4", "Select Fourth Firm Characteristic for your new index:", choices = acceptaple_features2,selected = "None", width = "1000px")
```

selectInput("characteristic_irats5", "Select Fifth Firm Characteristic for your new index:", choices = acceptaple_features2,selected = "None", width = "1000px")
```

selectInput("characteristic_irats6", "Select Sixth Firm Characteristic for your new index:", choices = acceptaple_features2,selected = "None", width = "1000px")
```

selectInput("quantile_used_ind","Enter the quantile to use to define the 0 (Low), 1 (middle), 2 (High) scores for each of the selected characteristics:", choices = 0.02*(1:20), selected = "0.2", width = "1000px")
```

@@

  thefeature = DATASET$SDC[[which(names(DATASET$SDC) == input$characteristic_irats1)]]  
  High_feature_events1 = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
  Low_feature_events1 = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature))

@@

  if (input$characteristic_irats2 != "None"){
    thefeature = DATASET$SDC[[which(names(DATASET$SDC) == input$characteristic_irats2)]]  
    High_feature_events2 = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
    Low_feature_events2 = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
  }
  if (input$characteristic_irats3 != "None"){
    thefeature = DATASET$SDC[[which(names(DATASET$SDC) == input$characteristic_irats3)]]  
    High_feature_events3 = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
    Low_feature_events3 = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
  }
  if (input$characteristic_irats4 != "None"){
    thefeature = DATASET$SDC[[which(names(DATASET$SDC) == input$characteristic_irats4)]]  
    High_feature_events4 = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
    Low_feature_events4 = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
  }
  if (input$characteristic_irats5 != "None"){
    thefeature = DATASET$SDC[[which(names(DATASET$SDC) == input$characteristic_irats5)]]  
    High_feature_events5 = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
    Low_feature_events5 = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
  }
  if (input$characteristic_irats6 != "None"){
    thefeature = DATASET$SDC[[which(names(DATASET$SDC) == input$characteristic_irats6)]]  
    High_feature_events6 = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
    Low_feature_events6 = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
  }

@@

feature_IRATStable_index <- reactive({

  thefeature = Index_Score_rect()

  High_feature_events = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_all)) & !is.na(thefeature))
  Low_feature_events = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_all)) & !is.na(thefeature))

  res = round(cbind(
    car_table(DATASET$returns_by_event_monthly[,Low_feature_events], DATASET$SDC$Event.Date[Low_feature_events], Risk_Factors_Monthly)$results,
    car_table(DATASET$returns_by_event_monthly[,High_feature_events], DATASET$SDC$Event.Date[High_feature_events], Risk_Factors_Monthly)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
  res
})

High_feature_Hedged_react_index <- reactive({
  thefeature = Index_Score_rect()
  High_feature_events = which(scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_all)) & !is.na(thefeature))
  High_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", High_feature_events,  DATASET$DatesMonth, DATASET$returns_by_event_monthly,event=1),1,non_zero_mean)
  remove_initialization_time(suppressWarnings(scrub(alpha_lm(High_feature,Risk_Factors_Monthly[,pnl_hedge_factors],hedge_months,trade=1))),min_date=FirstTrade)
})

>>>>

---
title: "Share Buyback and Equity Issue Anomalies Revisited: Interactive Tool"
author: "[Theodoros Evgeniou](http://faculty.insead.edu/theodoros-evgeniou/), [Enric Junque de Fortuny](ciri.be/), [Nick Nassuphis](https://www.linkedin.com/in/nick-nassuphis-8029372), and [Theo Vermaelen](http://faculty.insead.edu/theo-vermaelen/)"
output:  
  html_document:
    fig_width: 6
    fig_height: 2.5
    fig_align: center
runtime: shiny
---

@@

DATASET_INI = BUYBACK_DATA$DATASET
DATASET_INI$SDC = as.data.frame(DATASET_INI$SDC)
```

**NOTE:** Please always wait until all tables load (and "fade in")...

This is an interactive tool for the article [Share Buyback and Equity Issue Anomalies Revisited](). Users can explore the effects of various parameters as well as data filtering choices. For any given choices, users can generate and download a new **customized pdf version of the paper** by clicking the button below at any time. Note that it may take a couple of minutes to create and download the new paper.
<br>
<br>

```{r, fig.width=6, fig.height=5,echo=FALSE}
downloadHandler(
  filename = "report.pdf",
  content = function(file) {
    cat("knitting")
    #knitr::knit("report.Rnw",envir=environment())
    cat("texing")
    #tools::texi2pdf("report.tex")
    knitr::knit2pdf("report.Rnw",envir=globalenv())
    #toremove <- c("report.aux","report.bbl","report.blg","report.log","report.out")
    #file.remove(normalizePath(toremove))
    cat("done")
    file.rename(normalizePath('report.pdf'), file)
  }
)
```

<hr>
<hr>

### Dataset Filtering

You can select some filters for the dataset. All analyses below will be done only for the companies that are selected.

Every time you change these filters you may **need to wait a few seconds** until all results of this tool are updated (all tables/figures "fade in").

Select the time period for which you would like to do the analyses below:

```{r, eval=TRUE, echo = FALSE}
dateInput("startdate", "Starting Date:", 
          value = min(DATASET_INI$SDC$Event.Date) - 10, min = min(DATASET_INI$SDC$Event.Date), max = max(DATASET_INI$SDC$Event.Date)-3*370,
          startview = "year",
          width='100%')
```
<br>
```{r, eval=TRUE, echo = FALSE}
dateInput("enddate", "End Date (allow at least 3 years from the starting day you selected - else it will automatically use data up to 3 years after your start date):", 
          value = max(DATASET_INI$SDC$Event.Date) + 10, 
          min = min(DATASET_INI$SDC$Event.Date)+3*370, 
          max = max(DATASET_INI$SDC$Event.Date)+10,startview = "year",
          width='100%')
```

Selet the minimum size of the firms (in $millions) for which you would like to do the analyses below. The maximum selected should be larger than the minimum, else the maximum is automatically set to 10e6:

```{r, eval=TRUE, echo = FALSE}
selectInput("market_cap_min","Enter the Minimum Market Cap allowed (in millions):", choices = as.character(c(0,50*(1:20), 500*(1:20))), selected = "0", width = "1000px")
```
<br>
```{r, eval=TRUE, echo = FALSE}
selectInput("market_cap_max","Enter the Maximum Market Cap allowed (in millions):", choices = as.character(c(0,50*(1:20), 500*(1:20), ceiling(max(DATASET_INI$SDC$Market.Cap)))), selected = as.character(ceiling(max(DATASET_INI$SDC$Market.Cap))), width = "1000px")
```

```{r, eval=TRUE, echo = FALSE}
DATASET_NEW <- reactive({
  starting = input$startdate 
  ending = input$enddate   
  if (ending - starting < 3*365)
    ending = starting + 3*365

  market_cap_min = as.numeric(input$market_cap_min)
  market_cap_max = as.numeric(input$market_cap_max)
  if (market_cap_max < market_cap_min)
    market_cap_max = ceiling(max(DATASET_INI$SDC$Market.Cap))

  useonly_report = which(DATASET_INI$SDC$Event.Date >= starting & DATASET_INI$SDC$Event.Date <= ending & scrub(DATASET_INI$SDC$Market.Cap) >= market_cap_min & scrub(DATASET_INI$SDC$Market.Cap) <= market_cap_max)

  list(
    returns_by_event_monthly = DATASET_INI$returns_by_event_monthly[,useonly_report],
    DatesMonth = DATASET_INI$DatesMonth[,useonly_report],
    SDC = DATASET_INI$SDC[useonly_report,]
    #returns_by_event_monthly = DATASET_INI$returns_by_event_monthly,
    #DatesMonth = DATASET_INI$DatesMonth,
    #SDC = DATASET_INI$SDC
  )
})
```

<hr>
<hr>

This tool allows the user to explore descriptive statistics of some of the key firm characteristics. When the name of the firm characteristics ends with ".Score" it is  either the 1-5 score relative to the Fama-French breakpoints (e.g. for Size, Prior returns, and BE/ME ratio) or the percentile relative to all firms in the CRSP universe at the time of the buyback announcement, as discussed in the paper. Otherwise it is the raw value of the firm characteristic.

fluidPage(
  selectInput("characteristic", "Select Firm Characteristic:", choices = acceptaple_features,selected = acceptaple_features[1]),
  mainPanel(
    tabsetPanel("Example",
                tabPanel("Histogram",
                         renderPlot({
                           feature = DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic)]]
                           feature = feature[!is.na(feature)]
                           if (!is.numeric(feature))
                             feature = 1
                           hist(feature, density = 100, breaks = 100)
                         })),
                tabPanel("Summary Statistics",
                         renderDataTable({
                           feature = DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic)]]
                           #feature = feature[!is.na(feature)]
                           if (length(unique(feature)) > 20 & is.numeric(feature)){
                             res = t(as.matrix(summary(feature)))
                             colnames(res) <- c("Minimum", "1st Quantile", "Median", "Mean", "3rd Quantile", "Max")
                           }
                           if (is.character(feature) | length(unique(feature)) <= 20){
                             tmp = sort(table(feature), decreasing = TRUE)
                             res = t(as.matrix(tmp))
                           }
                           as.data.frame(res)
                           #m1<-gvisTable(show_data,options=list(showRowNumber=TRUE,width=1220, height=min(400,27*(nrow(show_data)+1)),allowHTML=TRUE,page='disable'))
                           #print(m1,'chart')
                         })
                )
    ),style='width: 100%;'))
```

<hr>
<hr>

### Industry Robustness Analysis of U-Index

Two types of robustness analysis has been considered in the paper: over different time periods, and across industries. We can select industries to remove here (make sure there are enough data left for the analysis):

```{r, eval=TRUE, echo = FALSE}
checkboxGroupInput("industry", "Select Industries  to remove:", choices = unique(DATASET_INI$SDC$Industry),selected = "Software",inline=TRUE)

@@

```{r, eval=TRUE, echo = FALSE}

feature_IRATStable_industry <- reactive({
  useonly_industry = !(DATASET_NEW()$SDC$Industry %in% input$industry) 
  res = round(cbind(
    car_table(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], DATASET_NEW()$SDC$Event.Date[useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], Risk_Factors_Monthly)$results,
    car_table(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued], DATASET_NEW()$SDC$Event.Date[useonly_industry& DATASET_NEW()$SDC$company_subset_undervalued], Risk_Factors_Monthly)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
  as.data.frame(res)
})

feature_CALtable_industry <- reactive({
  useonly_industry = !(DATASET_NEW()$SDC$Industry %in% input$industry) 
  res = round(cbind(
    calendar_table(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], DATASET_NEW()$SDC$Event.Date[useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], Risk_Factors_Monthly)$results,
    calendar_table(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued], DATASET_NEW()$SDC$Event.Date[useonly_industry& DATASET_NEW()$SDC$company_subset_undervalued], Risk_Factors_Monthly)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAL", "t-stat","p-value", "High: CAL", "t-stat","p-value")
  as.data.frame(res)
})

fluidPage(
  mainPanel(
    tabsetPanel("Example",
                tabPanel("Five-Factor IRATS Cumulative Abnormal Returns",
                         renderTable({
                           feature_IRATStable_industry()
                         })),
                tabPanel("Five-Factor Calendar Method Monthly Abnormal Returns",
                         renderTable({
                           feature_CALtable_industry()
                         }))    
    ),style='width: 100%;'))
```

<hr>
<hr>

@@

The article relates 5 firm characteristics (pre-buyback-announcement returns, idiosyncratic volatility, and volatility, as well as BE/ME and Firm Size). This tool allows the user to study the effects of combining any of these firm characteristics, as well as some other ones not discussed in the paper.

@@

selectInput("characteristic_irats", "Select Firm Characteristic to Define High/Low Firms:", choices = acceptaple_features1,selected = acceptaple_features1[1], width = "1000px")

selectInput("quantile_used","Enter the quantile to use to define High and Low Firms:", choices = 0.02*(1:20), selected = "0.2", width = "1000px")

checkboxInput("characteristic_irats_sign", "If you would like to change the sign of the firm characteristic (Low will be High and vice versa), select here:", value = FALSE, width = "1000px")

feature_IRATStable <- reactive({
  thesign = ifelse(input$characteristic_irats_sign, -1, +1)
  thefeature = thesign*DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats)]]  
  High_feature_events = which(scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used)) & !is.na(thefeature))
  Low_feature_events = which(scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used)) & !is.na(thefeature))
  res = round(cbind(
    car_table(DATASET_NEW()$returns_by_event_monthly[,Low_feature_events], DATASET_NEW()$SDC$Event.Date[Low_feature_events], Risk_Factors_Monthly)$results,
    car_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events], DATASET_NEW()$SDC$Event.Date[High_feature_events], Risk_Factors_Monthly)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
  as.data.frame(res)
})

feature_CALtable <- reactive({
  thesign = ifelse(input$characteristic_irats_sign, -1, +1)
  thefeature = thesign*DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats)]]  
  High_feature_events = which(scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used)) & !is.na(thefeature))
  Low_feature_events = which(scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used)) & !is.na(thefeature))
  res = round(cbind(
    calendar_table(DATASET_NEW()$returns_by_event_monthly[,Low_feature_events], DATASET_NEW()$SDC$Event.Date[Low_feature_events], Risk_Factors_Monthly)$results,
    calendar_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events], DATASET_NEW()$SDC$Event.Date[High_feature_events], Risk_Factors_Monthly)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAL", "t-stat","p-value", "High: CAL", "t-stat","p-value")
  as.data.frame(res)
})

High_feature_Hedged_react <- reactive({
  thefeature = DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats)]]  
  High_feature_events = which(scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used)) & !is.na(thefeature))
  High_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", High_feature_events,  DATASET_NEW()$DatesMonth, DATASET_NEW()$returns_by_event_monthly,event=1),1,non_zero_mean)
  remove_initialization_time(suppressWarnings(scrub(alpha_lm(High_feature,Risk_Factors_Monthly[,pnl_hedge_factors],hedge_months,trade=1))),min_date=FirstTrade)
})

Low_feature_Hedged_react <- reactive({
  thefeature = DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats)]]  
  Low_feature_events = which(scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used)) & !is.na(thefeature))
  Low_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", Low_feature_events,  DATASET_NEW()$DatesMonth, DATASET_NEW()$returns_by_event_monthly,event=1),1,non_zero_mean)
  remove_initialization_time(suppressWarnings(scrub(alpha_lm(Low_feature,Risk_Factors_Monthly[,pnl_hedge_factors],hedge_months,trade=1))),min_date=FirstTrade)  
})

@@

```{r, eval=TRUE, echo = FALSE}
fluidPage(
  mainPanel(
    tabsetPanel("Example",
                tabPanel("Five-Factor IRATS Cumulative Abnormal Returns",
                         renderTable({
                           feature_IRATStable()
                         })),
                tabPanel("Five-Factor Calendar Method Monthly Abnormal Returns",
                         renderTable({
                           feature_CALtable()
                         })),
                tabPanel("Cumulative Abnormal Returns,High, 12m hold",
                         renderDygraph({
                           pnl_plot_interactive(High_feature_Hedged_react())
                         })),
                tabPanel("Cumulative Abnormal Returns,Low, 12m hold",
                         renderDygraph({
                           pnl_plot_interactive(Low_feature_Hedged_react())
                         })),
                tabPanel("Monthly and Yearly Returns, High, 12m hold",
                         renderUI({
                           renderHeatmapX(pnl_matrix(High_feature_Hedged_react()))
                         })),
                tabPanel("Monthly and Yearly Returns, Low, 12m hold",
                         renderUI({
                           renderHeatmapX(pnl_matrix(Low_feature_Hedged_react()))
                         }))
    ),style='width: 100%;'))
```

<hr>
<hr>

### Customized Buyback Index

Much like the EU-index in the paper, one can create other indices by combining different firm characteristics as needed.

@@

<br>
```{r, eval=TRUE, echo = FALSE}
selectInput("characteristic_irats1", "Select First Firm Characteristic for your new index:", choices = acceptaple_features2,selected = acceptaple_features2[1], width = "1000px")
checkboxInput("characteristic_irats1_sign", "If you would like to change the sign of this firm characteristic (Low will be High and vice versa), select here:", value = FALSE, width = "1000px")
```

<br>
```{r, eval=TRUE, echo = FALSE}
selectInput("characteristic_irats2", "Select Second Firm Characteristic for your new index:", choices = acceptaple_features2,selected ="None", width = "1000px")
checkboxInput("characteristic_irats2_sign", "If you would like to change the sign of this firm characteristic (Low will be High and vice versa), select here:", value = FALSE, width = "1000px")
```

<br>
```{r, eval=TRUE, echo = FALSE}
selectInput("characteristic_irats3", "Select Third Firm Characteristic for your new index:", choices = acceptaple_features2,selected = "None", width = "1000px")
checkboxInput("characteristic_irats3_sign", "If you would like to change the sign of this firm characteristic (Low will be High and vice versa), select here:", value = FALSE, width = "1000px")
```

<br>
```{r, eval=TRUE, echo = FALSE}
selectInput("characteristic_irats4", "Select Fourth Firm Characteristic for your new index:", choices = acceptaple_features2,selected = "None", width = "1000px")
checkboxInput("characteristic_irats4_sign", "If you would like to change the sign of this firm characteristic (Low will be High and vice versa), select here:", value = FALSE, width = "1000px")
```

<br>
```{r, eval=TRUE, echo = FALSE}
selectInput("characteristic_irats5", "Select Fifth Firm Characteristic for your new index:", choices = acceptaple_features2,selected = "None", width = "1000px")
checkboxInput("characteristic_irats5_sign", "If you would like to change the sign of this firm characteristic (Low will be High and vice versa), select here:", value = FALSE, width = "1000px")
```

<br>
```{r, eval=TRUE, echo = FALSE}
selectInput("characteristic_irats6", "Select Sixth Firm Characteristic for your new index:", choices = acceptaple_features2,selected = "None", width = "1000px")
checkboxInput("characteristic_irats6_sign", "If you would like to change the sign of this firm characteristic (Low will be High and vice versa), select here:", value = FALSE, width = "1000px")
```

<br>
```{r, eval=TRUE, echo = FALSE}
selectInput("quantile_used_ind","Enter the quantile to use to define the 0 (Low), 1 (middle), 2 (High) scores for each of the selected characteristics:", choices = 0.02*(1:20), selected = "0.2", width = "1000px")
```

@@

  thesign = ifelse(input$characteristic_irats1_sign, -1, +1)
  thefeature = thesign*DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats1)]]  
  High_feature_events1 = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
  Low_feature_events1 = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature))

@@

  if (input$characteristic_irats2 != "None"){
    thesign = ifelse(input$characteristic_irats2_sign, -1, +1)
    thefeature = thesign*DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats2)]]  
    High_feature_events2 = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
    Low_feature_events2 = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
  }
  if (input$characteristic_irats3 != "None"){
    thesign = ifelse(input$characteristic_irats3_sign, -1, +1)
    thefeature = thesign*DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats3)]]  
    High_feature_events3 = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
    Low_feature_events3 = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
  }
  if (input$characteristic_irats4 != "None"){
    thesign = ifelse(input$characteristic_irats4_sign, -1, +1)
    thefeature = thesign*DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats4)]]  
    High_feature_events4 = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
    Low_feature_events4 = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
  }
  if (input$characteristic_irats5 != "None"){
    thesign = ifelse(input$characteristic_irats5_sign, -1, +1)
    thefeature = thesign*DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats5)]]  
    High_feature_events5 = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
    Low_feature_events5 = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
  }
  if (input$characteristic_irats6 != "None"){
    thesign = ifelse(input$characteristic_irats6_sign, -1, +1)
    thefeature = thesign*DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats6)]]  
    High_feature_events6 = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
    Low_feature_events6 = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
  }

@@

feature_IRATStable_index <- reactive({
  thefeature = Index_Score_rect()
  High_feature_events = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_all)) & !is.na(thefeature))
  Low_feature_events = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_all)) & !is.na(thefeature))
  res = round(cbind(
    car_table(DATASET_NEW()$returns_by_event_monthly[,Low_feature_events], DATASET_NEW()$SDC$Event.Date[Low_feature_events], Risk_Factors_Monthly)$results,
    car_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events], DATASET_NEW()$SDC$Event.Date[High_feature_events], Risk_Factors_Monthly)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
  res
})

feature_CALtable_index <- reactive({
  thefeature = Index_Score_rect()
  High_feature_events = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_all)) & !is.na(thefeature))
  Low_feature_events = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_all)) & !is.na(thefeature))
  res = round(cbind(
    calendar_table(DATASET_NEW()$returns_by_event_monthly[,Low_feature_events], DATASET_NEW()$SDC$Event.Date[Low_feature_events], Risk_Factors_Monthly)$results,
    calendar_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events], DATASET_NEW()$SDC$Event.Date[High_feature_events], Risk_Factors_Monthly)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAL", "t-stat","p-value", "High: CAL", "t-stat","p-value")
  res
})
